\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tabularx,}

\title{Ankeit Taksh}
\date{}
\begin{document}

\maketitle 

\textbf{Email:} ankeit.taksh@gmail.com  \textbf{Phone:} +65-81148011 \textbf{LinkedIn:} \href{https://www.linkedin.com/in/ankeittaksh}{LinkedIn} \textbf{GitHub:} \href{https://github.com/aktaksh}{Github}

\section*{Summary:}
A Linux Engineer with 14+ years of experience in the DevOps and SRE field. My work revolves around on-prem, cloud, and hybrid infrastructure with new projects and their operations. It includes hardware, low-latency high-performance systems, networking, documentation, and info-sec aspects. 

\section*{Education:}
 \textbf{National University of Singapore} {& M.Tech  2019 - 2021} \\
 \textbf{Dr MGR University} & B.Tech 2004 - 2008 
 
\section*{Certifications:}
{Redhat Certified Engineer} \hfill {Azure DevOps Expert } \\
{ Certified Kubernetes Administrator (CKA)} \hfill {Redhat OpenShift Specialist}

\section*{Professional experience:}
\subsection*{Senior DevOps Engineer \hfill {Telepathy Labs.AI, Singapore, Oct 2021 - current}} 
\textbf {TechStack:} {Linux, Kubernetes, AWS, Bash, Terraform, Jenkins, TeamCity, ArgoCD, RDS, EKS, ECS Route53, S3, DataDog, Grafana, SOC, VPC, HELM} 
\begin{itemize}[leftmargin=*]
 \item Escalation Lead for operational incidents and responsible for the implementation of new projects.
 \item Tune in Linux distros and ensure SOC compliance and hardening is met.
 \item Ensure High availability design and Disaster recovery is in place while ensuring the least downtime.
 \item Key Projects:
  \begin{itemize}[label=--, leftmargin=*]
    \item Project Stella Automotive: Host ML-based solution on AWS using EKS, ECS and other AWS resources
    \item Migrate CI/CD pipelines: Setup entire project via HELM and Argocd
  \end{itemize}
\end{itemize}


\subsection*{Senior DevOps Engineer \hfill Biqmind, Singapore, Oct 2019 - Oct-2021}
  \textbf{Techstack:} Ubuntu, Centos, RHEL, Azure, AWS, Digital Ocean, Ansible, HELM, GOCD, GITOPS, Linux, OpenShift, OKD, Kubernetes, Docker, Prometheus, Grafana, Dell Rack, Dell Storage, Shell script, Python, KVM, AIML
\begin{itemize}[leftmargin=*]
\item Lead and mentor a closely knit team of DevOps and SRE professionals, implementing new DevOps and SRE solutions to shape client experience.
  \item Develop, support, and administer business-critical infrastructure, blending engineering and operational responsibilities.
  \item Active trainer for Microsoft Azure Kubernetes and OpenShift, as well as content creator of workshops. Innovate integrated solutions for client applications and train resources.
  \item Key Projects:
  \begin{itemize}[label=--, leftmargin=*]
    \item Project for Rapiscan: Migrated ML solution from monolithic to Kubernetes-based microservices across multiple airports.
    \item OpenShift and datacentre migration: Moved Biqmind from Jakarta to Singapore with storage and network hardware.
    \item CI/CD pipelines: Enhanced productivity by 2 hours per developer per day for LanternEdge Dev and HW team.
    \item In-house Virtualization platform: Designed using Ovirt and Redhat Enterprise Virtualization.
  \end{itemize}

\end{itemize}

\subsection*{Technical Lead \hfill  SGX, Singapore (Contract) | Mar 2016 - Jul 2019}
  \textbf{Techstack:} RHEL, AWS, Ansible, Linux, OpenShift, Kubernetes, Docker, Grafana, HP servers, Dell Rack, Storage, Shell script, Python, Veritas, HP tools, Atlassian
\begin{itemize}[leftmargin=*]
  \item Delivered architectural and practical cloud and infra solutions to improve CI/CD, resiliency, efficiency, performance, and cost-saving.
  \item Monitored and reported on service level objectives to stakeholders, working with business and product owners for project design.
  \item Capacity planning and management, creating and maintaining a capacity model for on-prem and AWS hosting based on user flow profiles.
  \item Led engineering projects for DevOps, SRE, and DC infrastructure, including release systems, CI/CD workflows, and datacentre infrastructure.
  \item Mentored SRE teams for production control, delivered projects from a technical perspective to go-live, and implemented automated provisioning and configuration management.
  \item Key Projects:
  \begin{itemize}[label=--, leftmargin=*]
    \item SGX-TITAN: Led a derivatives trading project, building an ultra low latency, high-resiliency infrastructure.
    \item SGX-OpenShift: Setup a 27-node multi-cluster for critical applications involving DevOps, Jenkins, Kubernetes, Docker, Ansible, OCP.
    \item SGX Clearing Engine: Implemented a high-resiliency, application HA solution with 20 nodes using Veritas clusters.
  \end{itemize}
\end{itemize}

\subsection*{Technical Lead \hfill  Maybank, Singapore (Contract) | Jul 2019 - Nov 2019}
\begin{itemize}[leftmargin=*]
  \item Accountable for in-house platform engineering, delivering scalable and disaster-resilient solutions.
  \item Analyzed new solutions for infrastructure upgrades, developed architectural and implementation plans, primarily based on Redhat recipes.
  \item Key Points:
  \begin{itemize}[label=--, leftmargin=*]
    \item Led adoption of Cyber Security aligned with CI/CD practices.
    \item Provided Kubernetes microservices infrastructure integrated with Cloud.
    \item Participated in system design, capacity planning, and platform management.
    \item Ensured Security and compliance for bank’s trading platform.
    \item Set up Redhat satellite for patching standards.
  \end{itemize}
\end{itemize}


\subsection*{System Engineer \hfill  ANTlabs, Singapore | Jun 2015 - Feb 2016}
\begin{itemize}[leftmargin=*]
  \item Collaborated with a team of networking experts to build Networking gateways from bare metal.
  \item Maintained standard build practices and performed kernel and network-based systems tuning.
  \item Interfaced with project sponsoring groups to gather requirements and managed implementation and post-implementation project support.
  \item Monitored, evaluated, and resolved hardware and/or software-related performance issues.
  \item Utilized standard tools for provisioning, configuration management, and automation based on shell scripting.
  \item Key Project:
  \begin{itemize}[label=--, leftmargin=*]
    \item Lead implementation engineer for Etisalat WIFI project, covering Abu Dhabi and Dubai regions, serving users with Wifi offloading solution across 1000+ wifi points. Implemented high availability solution for seamless internet connection.
  \end{itemize}
  \item Environment: Linux, Dell, HP servers, Networking Gateways, VLANs, Advanced Networking, Huawei Storage, Shell script, PHP, SQL
\end{itemize}


\subsection*{Tech Support Engineer       \hfill    Altisource, India | Dec2 013 - Jan 2015}
\begin{itemize}[leftmargin=*]
  \item As a LINUX admin Provided day-to-day support for production Infrastructure and Applications.
  \item Proactively supported all applications, including database maintenance, logging, and monitoring.
  \item Documented, installed, and tested patches, ensured compliance with Group and ISO standards for applications and Infrastructure.
  \item Proactively identified and proposed infrastructure and applications improvements.
  \item Developed and maintained a knowledge base and documentation for security and support of Infrastructure and applications.
\end{itemize}

\subsection*{Sr Tech Executive \hfill   NTTDATA, India | Jul 2013 - Nov 2013}
\begin{itemize}
    \item As a LINUX admin responsible for handling escalated incidents and High Availability environment incident management on UNIX Platform [LINUX, Solaris].
    \item Problem Management on UNIX platform. Perform Root Cause Analysis using quality tools.
    \item Change and incident management for application support.
\end{itemize}

\subsection*{Senior Analyst \hfill HCL, India | Dec 2009 - Jun 2013}
\begin{itemize}
    \item Responsible for handling escalated incidents and High Availability environment incident management on UNIX Platform [HPUX, LINUX, Solaris].
    \item Problem Management on UNIX platform. Perform Root Cause Analysis.
    \item Change Management: Prepare Implementation, backout, and test plan for Change records.
    \item Perform risk and impact analysis for changes.
\end{itemize}

\subsection*{Tech Support Executive \hfill Sutherland, India | Sep 2008 - Dec 2009}
\begin{itemize}
    \item Engineer responsible for handling user issues for Microsoft Windows Vista and Dual OS Linux users.
    \item Resolve desktop and network support of all kinds for users.
    \item Handle Calls and voice support for multiple users for Vista patching Issue.
\end{itemize}
\end{document}
